Clean 2015 Raw Data

### 2018-11-02 analysis/2017 APPS abstract/README.Rmd
Replace more "flooded" with "puddled"

In order to understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes in the dry seasons of 2015 and 2016. The main plot irrigation treatments in both experiments were: puddled, maintaining 10cm standing water through the season and alternate wetting and drying (AWD), a water saving technology developed by the International Rice Research Institute (IRRI) and partners as adaptation strategy for water-scarce environments. In 2015 the split plots were nitrogen (N) applications applied as 0 kg ha-1, 120 kg ha–1, and 150 kg ha–1 total N. In 2016 changes were made to address issues discovered in 2015. In 2016 split plots were N applications at 60 kg ha-1 and 180 kg ha-1 total N. Nitrogen was applied in splits in both seasons.

>>>>

In order to understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes in the dry seasons of 2015 and 2016. The main plot irrigation treatments in both experiments were: flooded, maintaining 10cm standing water through the season and alternate wetting and drying (AWD), a water saving technology developed by the International Rice Research Institute (IRRI) and partners as adaptation strategy for water-scarce environments. In 2015 the split plots were nitrogen (N) applications applied as 0 kg ha-1, 120 kg ha–1, and 150 kg ha–1 total N. In 2016 changes were made to address issues discovered in 2015. In 2016 split plots were N applications at 60 kg ha-1 and 180 kg ha-1 total N. Nitrogen was applied in splits in both seasons.

### 2018-11-02 data-raw/README.Rmd
Revert "Remove TRT from data"
This reverts commit 0ef1212ad5f9cc39d60170add9de06a3e5dde5cd.
Update static docs
Replace more "flooded" with "puddled"

@@

# Replace "Flooded" with "FLD" -------------------------------------------------
DS2016$WMGT[which(DS2016$WMGT == "Flooded")] = "FLD"

@@

>>>>

*Note* TRT is created here as a combination of the main plot/split plot
treatment. This is used in place of plot numbers to keep the data in order.
However, it is not used in the final analysis as a treatment effect.

@@

@@

# Arrange NRTE values
AUDPS$NRTE <-
  forcats::fct_relevel(AUDPS$NRTE,
                       "N0",
                       "N100",
                       "N120",
                       "N60",
                       "N180")
